Cross-validation of regression models: mixed model examples (edited v3)

### 2024-09-13 scratch/JSS-submission/Revision-1/Fox-Monette-cv-package.Rmd
replace selectedModel() with cvInfo.cvSelect() method

Applying \code{selectModelList()} to the \code{Auto} polynomial-regression models, and using 10-fold CV, we obtain:
```{r recursive-CV-polynomials}
recursiveCV.auto <- cv(selectModelList, data = Auto, 
                       working.model = mlist, save.model = TRUE, 
                       seed = 2120)
summary(recursiveCV.auto)
brief(m.sel <- selectedModel(recursiveCV.auto))
cv(m.sel, seed = 2120)
```
As expected, recursive CV produces a larger estimate of MSE for the selected 7th degree polynomial model than CV applied directly to this model (using the same seed for \proglang{R}'s random-number generator to obtain the same folds).

>>>>

Applying \code{selectModelList()} to the \code{Auto} polynomial-regression models, and using 10-fold CV, we obtain:
```{r recursive-CV-polynomials}
recursiveCV.auto <- cv(selectModelList, data = Auto, 
                       working.model = mlist, save.model = TRUE, 
                       seed = 2120)
summary(recursiveCV.auto)
brief(m.sel <- cvInfo(recursiveCV.auto, "selected model"))
cv(m.sel, seed = 2120)
```
As expected, recursive CV produces a larger estimate of MSE for the selected 7th degree polynomial model than CV applied directly to this model (using the same seed for \proglang{R}'s random-number generator to obtain the same folds).
